\section{Prior Work}

While there are large bodies of work on both graphical models and thermal modeling of buildings, the intersection of these areas does not have much substantial literature.
Most approaches to thermal modeling of buildings are driven by simulations of varying detail and fidelity.
Much of this is due to the lack of detailed temperature data in buildings.
As of 2012, only 14\% of the buildings in the U.S. deployed building management systems (BMS), which are capable of storing temperature trend data for use in building empirical models~\cite{cbecs2012}.
However, the temperature data that \emph{is} available from BMS or otherwise from networked thermostats such as the Nest is often only at the granularity of individual HVAC zones, which we have established is insufficient for maintaining comfort in a building.

\cite{kusiak2010modeling} explores a family of data-driven approaches to HVAC modeling, focusing on support vector machines and multi-layer perceptrons for predicting energy expenditure under different HVAC control parameters.
While effective from a predictive standpoint, their models do not actually account for occupant comfort in the building, instead making the same broken assumption that temperature is uniform across an HVAC zone.

\cite{afram2014review} presents a survey of modeling methods for HVAC systems, comparing physics-based simulation methods with data-driven statistical approaches.
It concludes that physics based models generalize well, but typically have poor accuracy compared to data-driven approaches; however, it also finds that data-driven methods fail to generalize beyond whatever training data is available.
A further complication is that accurate thermal models require intimate knowledge of a building's construction such as the thickness and materials of the walls, windows, floors and ceilings.
As before, the concentration of the survey is to predict energy usage and temperature in HVAC systems rather than evaluating the validity of the structure of the HVAC system.

In the area of building science, there is a growing set of literature on how to infer the structure of an HVAC system. \cite{pritoni2015short} uses an intrusive method for determining which AHUs are connected to which VAVs.
By perturbing HVAC control parameters to induce changes in the HVAC zones, Pritoni et al can reconstruct the mapping of AHU to VAV to HVAC zone to room; in combination with deployed temperature sensors, this method could more accurately determine the strength of thermal coupling between microzones.
However, the intrusive nature of the method means this method cannot be applied to buildings where actuating HVAC setpoints is disallowed or impossible.
